\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-15 experience.tex
updates in case studies

- Advanced safety properties\\
- Handles intra-machine concurrency\\
- Writing the protocol while testing it (co-development)

The Live Azure Table Migration (MigratingTable) is a library for transparently migrating a data set between tables in an Azure Storage service, while an application is accessing this data set.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/livemigration}
\caption{Resharding a data set when a third Azure storage account is added. Two key ranges are each migrated to the new account using a MigratingTable instance (abbreviated MTable).}
\label{fig:livemigration}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/mocked_migration}
\caption{MigratingTable \psharp correctness test environment.}
\label{fig:mockedmigration}
\end{figure}

Since we were designing a new concurrent protocol that we expected to become increasingly complex over time as we add optimizations, we planned from the beginning to maintain a \psharp test harness along with the protocol to maintain confidence in its correctness.

@@

All of our input histories include two application processes.  Each process performs either a single streaming read or a sequence of two atomic calls, each a read or a batch write.  Each batch write call includes one or two operations, where the operation type is chosen from the set supported by IChainTable2 (Insert, Replace, Merge, Delete, InsertOrReplace, InsertOrMerge, DeleteIfExists) and the row key is chosen from $\{0, \ldots, 5\}$.  If the operation requires an If-Match value, it is equally likely to be \texttt{*}, the current ETag of the row (if it exists), or some non-matching value.  Finally, the new entity includes a user-defined property \texttt{isHappy} whose value is equally likely to be true or false.  For both atomic and streaming reads, the filter expression is equally likely to be empty (i.e., match everything), \texttt{isHappy eq true}, or \texttt{isHappy eq false}.

>>>>

The Live Azure Table Migration (MigratingTable) is a library for transparently migrating a data set between tables in an Azure Storage service, while an application is accessing this data set. This case study is interesting because its developers built the \psharp model of the system, while developing the library, to increase confidence in its implementation; indeed they discovered many bugs during this \emph{co-development} process (see Section~\ref{}). Another interesting aspect of this system is that it heavily uses the \texttt{async}/\texttt{await} primitives, which were not supported in the original \psharp runtime, and thus required us to extend \psharp with support for intra-machine concurrency (see Section~\ref{}). Finally, a lot of complex safety properties were written to test MigratingTable with \psharp, whereas the vNext model focused on a single liveness property.

@@

%\begin{figure}[t]
%\centering
%\includegraphics[width=\linewidth]{img/livemigration}
%\caption{Resharding a data set when a third Azure storage account is added. Two key ranges are each migrated to the new account using a MigratingTable instance (abbreviated MTable).}
%\label{fig:livemigration}
%\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/mocked_migration}
\caption{Environmental model of MigratingTable (each box with a dotted line represents one \psharp machine).}
\label{fig:mockedmigration}
\end{figure}

%Since we were designing a new concurrent protocol that we expected to become increasingly complex over time as we add optimizations, we planned from the beginning to maintain a \psharp test harness along with the protocol to maintain confidence in its correctness.

@@

%All of our input histories include two application processes.  Each process performs either a single streaming read or a sequence of two atomic calls, each a read or a batch write.  Each batch write call includes one or two operations, where the operation type is chosen from the set supported by IChainTable2 (Insert, Replace, Merge, Delete, InsertOrReplace, InsertOrMerge, DeleteIfExists) and the row key is chosen from $\{0, \ldots, 5\}$.  If the operation requires an If-Match value, it is equally likely to be \texttt{*}, the current ETag of the row (if it exists), or some non-matching value.  Finally, the new entity includes a user-defined property \texttt{isHappy} whose value is equally likely to be true or false.  For both atomic and streaming reads, the filter expression is equally likely to be empty (i.e., match everything), \texttt{isHappy eq true}, or \texttt{isHappy eq false}.
